---
title: "autoflowchart"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{autoflowchart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
devtools::load_all()
```


`autoflowchart` is a R package to help you build flowcharts for data management or cohort follow up.


To use it, download this repo then use:
- install it using `devtools::install_github("https://github.com/FrankwaP/autoflowchart")`
- or clone this repo and use `devtool::load_all("LOCAL_PATH_TO_THE_REPO")` (easier to debug or add modifications).

It writes down a [Graphviz](https://graphviz.org/) .dot file and call Graphviz.
So it must be installed and the `dot` command must exist in your system's `PATH`.

It considers:
 - the main branch, for which summaries of the datasets at each step are displayed
 - the side nodes, for which summaries of the modifications at each step are displayed

The summaries are obtained using functions which:
 - return a string or `NULL`
 - uses specific arguments:
   - for the datasets summaries: `df` and optionally `subject` and `time`
   - for the modifications summaries: `df1`, `df2` and optionally `subject` and `time`

Some functions are already coded, but you can defined yours as long as they respect these constraints.

Here is a basic example:

```{r}
```


```{r}
# example of data-management ----

## original dataset ----
data0 <- ChickWeight

#
title1 <- "remove outliers"
task1 <- compare_after_outliers_removal
data1 <- data0
idx <- (data1[["weight"]] < 50) | (data1[["weight"]] > 300)
data1[idx, "weight"] <- NA
#
title2 <- "remove incomplete observations"
task2 <- combine_comparaisons(
  compare_incomplete_observations,
  compare_subjects,
  compare_columns_with_na
)
data2 <- data1
data2 <- data2[complete.cases(data2), ]


# function to summarize the information of a dataset
summarize <- combine_summaries(summarize_nb_subjects, summarize_nb_observations)

# Generating the flowchart
make_flowchart(
  list_df = list(data0, data1, data2),
  list_summary_func = list(summarize, summarize, summarize),
  list_comparison_func = list(task1, task2),
  list_comparison_title = list(title1, title2),
  subject = "Chick",
  time = "Time",
  output_svg_file = "test-flowchart.svg"
)
```

```{r, eval=FALSE}
knitr::include_graphics("test-flowchart.svg")
```

```{r, echo=FALSE}
# to avoid a problem with README.Rmd which calls this vignette
if (!"IAMREADME" %in% names(environment())) {
  knitr::include_graphics("test-flowchart.svg")
}
```
